Review of Polymer Solutions for Near-Field Electrospinning with Spatial Control

### 2019-06-24 NFES_Review/article.tex
article new structure

\section{Polymer Solution and NFES Parameters}
To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited. Kameoka et al (2003) demonstrated that a small initial spinning radius can be achieved using an atomic force microscope tip with a small polymer solution drop at the tip. Near-field electrospinning, has exhibited to be capable fabricate nano fibers over and nano fiber patterns (Sun et al 2006). Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner. Using a spinneret with a reservoir (e.g. syringe) of solution generally produces fibers with diameter of a few micrometers [Gupta et al 2007; Xue et al 2014] since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through. Coppola et al (2014) have showned a NFES variant that allows polymer nano fibers to be deposited directly from a polymer drop,  averting the issue of nozzle clogging. The fibers are also prone soaking after deposition thus giving the fibers a semi-circular cross-section as depicted in Xue et al's (2014) work. The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al (2008) used a 100 \textmu m inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al (2013) used a \textmu m-diameter tip Tungsten spinneret in a 26 gauge needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).

@@

\subsection{Polymer Solution}In electrospinning, it is generally agreed that with higher concentration, the diameter of the fibers increased due to greater viscosity which resist stretching. In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased [Chang et al 2008; Zheng et al 2012]. However, in separate studies by Pan et al (2014) using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and Pan et al (2015) using polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration. Pan et al (2015) attributed this to a higher charge accumulation in higher concentration PVDF solution. However, more studies need to be carried out to verify this.

>>>>

\section{Polymer Solution}
In electrospinning, it is generally agreed that with higher concentration, the diameter of the fibers increased due to greater viscosity which resist stretching. In near field electrospinning, similar observations have been reported where concentration increases, fiber diameter increased [Chang et al 2008; Zheng et al 2012]. However, in separate studies by Pan et al (2014) using poly(\ensuremath{\gamma }-benzyl \ensuremath{\alpha }, l-glutamate) and Pan et al (2015) using polyvinylidene fluoride (PVDF) reported reduction in fiber diameter with increasing concentration. Pan et al (2015) attributed this to a higher charge accumulation in higher concentration PVDF solution. However, more studies need to be carried out to verify this.

\subsection{Polymers}

\subsection{Solvents}

\section{NFES Parameters}
To spin nano fibers at close distances, the initial diameter of the jet is required to be as small as possible since stretching of the thread is limited. Kameoka et al (2003) demonstrated that a small initial spinning radius can be achieved using an atomic force microscope tip with a small polymer solution drop at the tip. Near-field electrospinning, has exhibited to be capable fabricate nano fibers over and nano fiber patterns (Sun et al 2006). Nevertheless, having a small polymer solution drop at the nozzle tip limits the length of the fibers that can be fabricated in a continuous manner. Using a spinneret with a reservoir (e.g. syringe) of solution generally produces fibers with diameter of a few micrometers [Gupta et al 2007; Xue et al 2014] since it creates a limit to which the nozzle inner diameter can be reduced to allow the solution to flow through. Coppola et al (2014) have showned a NFES variant that allows polymer nano fibers to be deposited directly from a polymer drop,  averting the issue of nozzle clogging. The fibers are also prone soaking after deposition thus giving the fibers a semi-circular cross-section as depicted in Xue et al's (2014) work. The thinnest nozzles in literature so far are about 100 $\mu m $ in diameter, for instance Chang et al (2008) used a 100 \textmu m inner diameter needle tip to electrospin poly(ethylene oxide) (PEO) and Camillo et al (2013) used a \textmu m-diameter tip Tungsten spinneret in a 26 gauge needle to electrospin co-polymer, poly[2-methoxy-5-(2-ethylhexyloxy)-1,4-phenylenevinylene] (MEH-PPV) with poly(ethylene oxide) (PEO).

@@
